Renewal and stability in populations structured by remaining years of life

### 2016-11-29 ThanoRepro/ThanoRepro.tex
further tinkering with text around lotka renewal eq

\section*{Requisites of a years-left renewal model}
The Lotka-Leslie renewal model \citep{sharpe1911problem, leslie1945use} is
situated in a closed, unisex, homogenous population framework. With
parameters equated, the continuous form of the model contains a component for
survival, $\ell(a)$, a scaling factor for growth, $e^{-ra}$, and a component for fertility, $m(a)$:

\begin{equation}
\label{eq:lotka}
1 = \int_{a=0}^\infty l(a)e^{-ra}m(a)\dd a \ep
\end{equation}

Each of these elements is structured by
age, $a$. %The model can be approximated by observed data because
%age is typically known. % The survival function, $\ell(a)$, derives
%from a lifetable, usually based on age-specific event-exposure mortality rates,
%which require counts of decedents and an estimate of the
%population exposed to risk in the same chronological age classes.
Age in the growth factor, $e^{-ra}$, pertains to the passage of
time more than it does to chronological age (this is synchronous with birth
cohorts). The product of this growth factor and $\ell(a)$ gives a
function proportional to the stable age structure, $c(a)$, and it is often
intuitive to imagine these two elements together as one for this reason. Female
fertility rates, $m(a)$, are based on daughters born to mothers in this limited
single-sex model. The functions $m(a)$ and $\ell(a)$
together intuitively make for net female fertility, and their age-wise product
is sometimes written as $\phi(a)$. This model lends itself to commonly collected data because age
is typically known, and can be asked.
% For the two essential rate componenents underlying the renewal
 % equation~\eqref{eq:lotka}, classification by chronological age is essentially given--- it is deterministic in the sense that time passed since birth is typically known by individuals. The kinds of errors in such classification are mostly due to innumeracy, rounding, exaggeration, and similar kinds of biases, but even in such cases, chronological age is fundamentally knowable.

>>>>

\section*{Requisites of a years-left renewal model}
The Lotka-Leslie renewal model \citep{sharpe1911problem, leslie1945use} is
situated in a closed, unisex, homogenous population framework. The continuous form of the model contains a component for
survival, $\ell(a)$, a scaling factor for growth, $e^{-ra}$, and a component for
female fertility, $m(a)$:

\begin{align}
\label{eq:lotka}
B(t) &= \int_{0}^\infty B(t)\ell(a)e^{-ra}m(a)\dd a \ec \\
\intertext{or when parameters are equated}
1 &= \int_{0}^\infty \ell(a)e^{-ra}m(a)\dd a \ep
\end{align}

Each of these elements is structured by
age, $a$. %The model can be approximated by observed data because
%age is typically known. % The survival function, $\ell(a)$, derives
%from a lifetable, usually based on age-specific event-exposure mortality rates,
%which require counts of decedents and an estimate of the
%population exposed to risk in the same chronological age classes.
Age in the growth factor, $e^{-ra}$, pertains to the passage of
time more than it does to chronological age (this is synchronous with birth
cohorts). The product of this growth factor and $\ell(a)$ gives a
function proportional to the stable age structure, $c(a)$, and it is often
intuitive to imagine these two elements together as one for this reason. Female
fertility rates, $m(a)$, are based on daughters born to mothers in this limited
single-sex model.  The age-wise product of $m(a)$ and $\ell(a)$
can be interpreted as net female fertility, and this
is sometimes written as $\phi(a)$. As with most demographic models and
measures, this abstraction of renewal lends itself to
commonly collected data because age is typically known.
% For the two essential rate componenents underlying the renewal
 % equation~\eqref{eq:lotka}, classification by chronological age is essentially given--- it is deterministic in the sense that time passed since birth is typically known by individuals. The kinds of errors in such classification are mostly due to innumeracy, rounding, exaggeration, and similar kinds of biases, but even in such cases, chronological age is fundamentally knowable.
